Supplement to Spectral Variability of Two Rapidly Rotating Brown Dwarfs: \\2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010

### 2017-05-24 supplement.tex
added some discussion of optical depth of dust.

>>>>

\clearpage
\section{Optical Depth of Possible Haze Clouds}

\subsection{Lower limit Optical Depth}
Let's assume that there is a haze layer that covers 50\% of \shb's surface (ie. one hemisphere).
This will give us a lower limit on the optical depth to explain the variability amplitudes.
The flux after extinction is 
\begin{equation}
F_\mathrm{obs} = F_\mathrm{d} e^{-\tau}
\end{equation}
where $F_\mathrm{obs}$ is the observed flux, $F_\mathrm{d} $ is the flux from a deep layer underneath the haze and $\tau$ is the optical depth of the haze.
Under our assumption that the haze covers one hemisphere, the brighter hemisphere will have a flux $F_\mathrm{obs}  = F_\mathrm{d}$ so the maximum to minimum flux ratio is
\begin{equation}
f_R = e^{\tau}
\end{equation}
or
\begin{equation}
\tau = \ln{(f_R)}
\end{equation}
From the main paper, the relationship between variability amplitude and $f_R$ is
\begin{equation}\label{eq:ampFromRatio}
A  = \frac{f_R - 1}{f_R + 1}
\end{equation}
so
\begin{equation}
f_R = \frac{A + 1}{1 - A}.
\end{equation}
so
\begin{equation}
\tau = \ln{\left(\frac{A+1}{1 - A}\right)}
\end{equation}

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{images/optical_depth/tau_plot_lower.pdf}
\caption{Optical depth if the haze layer is assumed to cover a full hemisphere to explain the flux variations.}\label{fig:opticalDepthLower}
\end{centering}
\end{figure}

\subsection{Optical Depth for Assumed Spot Contrast}
